A dataset of Scratch programs,\\Scraped, Shaped and Scored

### 2017-02-16 MSR-Scratch.tex
Addition to enabled research

>>>>

Apart from quantitative studies, the dataset can support the design of experiments and field studies, whose material often includes Scratch programs with specific characteristics.
For example, in \cite{hermans_2016} examples of Scratch programs exhibiting specific smells were used in a controlled experiment to determine how the smells affected the understanding and the modification of the programs.
This queryable dataset can support finding example programs with characteristics according to the experiment design and the field of the study.
